Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-15 paper/main.tex
More thoughts

% title has to be < 110 chars incl. spaces
%  at the moment 109 Chars
\title{Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description}

@@

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% What we do
In the current study, we exploratorily tested if spatial information embedded in
a Hollywood movie and its audio-description of (i.e. the movie's soundtrack with
an additional narrator) correlates with increased hemodynamic activity in the
PPA.
%
We use publicly available functional magnetic resonance imaging data
(studyforrest.org) of 14 subjects to build canonical general linear model (GLM)
$t$-contrasts and compare current results to results that we gained from a
dedicated visual localizer experiment conducted with same participants.
% compare to visual localizer experiment group results
On a group average level, results of our whole brain analyses show significantly
increased activation restricted to the anterior part of the PPA that was defined
using the visual localizer [as well as in the retrosplenial and lateral
occipital cortex] of both hemispheres.
% individual results
On an individual level, results show significant bilateral clusters in the
anterior PPA of nine subjects and significant unilateral clusters in two
subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of auditorily presented spatial
information.
% conclusion: PPA has subregions
Lastly, our results provides further evidence that the PPA can be divided into
functional subregions.\end{abstract}

@@

>>>>

% title has to be < 110 chars incl. spaces
%  at the moment 109 Chars
\title{Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description}
%\title{Stimulus and paradigm selection impacts localization of "parahippocampal place area" (PPA)}

@@

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% What we do
In the current study, we exploratorily tested if spatial information embedded in
a Hollywood movie and its audio-description of (i.e. the movie's soundtrack with
an additional narrator) correlates with increased hemodynamic activity in the
PPA.
%
We use publicly available functional magnetic resonance imaging data
(studyforrest.org) of 14 subjects to build canonical general linear model (GLM)
$t$-contrasts and compare current results to results that we gained from a
dedicated visual localizer experiment conducted with same participants.
% compare to visual localizer experiment group results
On a group average level, results of our whole brain analyses show significantly
increased activation restricted to the anterior part of the PPA that was defined
using the visual localizer [as well as in the retrosplenial and lateral
occipital cortex] of both hemispheres.
% individual results
On an individual level, results show significant bilateral clusters in the
anterior PPA of nine subjects and significant unilateral clusters in two
subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of auditorily presented spatial
information.
% conclusion: PPA has subregions
Lastly, our results provides further evidence that the PPA can be divided into
functional subregions.

Key finding: We observe brain activation congruent with presumed PPA function
in the (anterior) location of the PPA, based on high-level semantic information
in an auditory stimulus.

\end{abstract}

@@

Question:
- how valid is localization of proposed PPA function given standard localizers?
- why three datasets?
  - VIS: connection to the literature; problem: stimulus validity re PPA function
  - AV: more valid stimulus (given real-world); problem operationalize PPA function (there is *one* way to do it)
  - AD: alternative stimulus for propsed function; similar but different operationalization problem
